---
title: "year_week_no: Data name"
date: "`r Sys.Date()`"
output: html_notebook
---

# TidyTuesday

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```

# Load the weekly Data

Load the weekly data into the `tt` object.

```{r Load}
year <- YY
week <- WW
dir_name <- paste0(year, "/", year, "_week_", week, "/")
file_name <- "str"

tt <- read_csv(here(paste0(dir_name, "data/", file_name, ".csv")))

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}
# Look at Data (top + bottom)
head(tt)
tail(tt)
```


```{r}
tibble::glimpse(tt)
```

Check column data type (e.g. numeric, character,...).
Are data and column classes correctly specified?  
If not, convert column class into the correct one.  

```{r}
summary(tt)
```

* Check Min, Max values.
Are they in a reasonable range?  
* How many NAs are there in each variable?  
* Is there anything "weird"?  

If column class is character, check:  
```{r}
tt %>% count(col_name)
```

Validating data with external information --> Check "weird stuff"  

# Wrangle

```{r Wrangle}



```

# Questions
My questions are ...
- q1
- q2

# Visualize

```{r Visualize}


  
```

# Save Image
Save image (.png), then share on twitter (maybe) using hashtag `#TidyTuesday`.

```{r}
ggsave("fig_name.png",
       fig_name)

```
